cardinalR: Generating interesting high-dimensional data structures

### 2025-04-20 paper-cardinalR.Rmd
Added additional function tabel initial

>>>>

```{r}
add_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_bkgnoise",
                            "randomize_rows",
                            "gen_nproduct",
                            "gen_nsum",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3",
                            "gen_rotation",
                            "gen_globalminmax",
                            "scale_data"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

```{r add-tb-html, eval=knitr::is_html_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", col.names = c("Function", "Explanation")) 
```

```{r add-tb-pdf, eval=knitr::is_latex_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
